---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
Loading the data from the zip file.
```{r loaddata}
file <- unz("activity.zip", "activity.csv")
activity <- read.csv(file)
```

What does it look like?
```{r str}
str(activity)
```

## What is mean total number of steps taken per day?
```{r histogram}
stepsperday <- tapply(activity$steps, activity$date, sum, na.rm = T)
hist(stepsperday, main = "Histogram of steps taken each day",
     xlab = "Total number of steps per day")
```

Mean and median of steps for each day
```{r meanmedian}
mean(stepsperday)
median(stepsperday)
```

## What is the average daily activity pattern?
```{r timeseries}
intervalmeans <- tapply(activity$steps, activity$interval, sum, na.rm = T)
plot(unique(activity$interval), intervalmeans, type = "l",
     xlab = "Time (5-minute intervals)", ylab = "Average number of steps taken",
     main = "Average daily activity pattern")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
maxsteps <- sort(intervalmeans, decreasing = T)[1]
```
8:35 with `r maxsteps[[1]]` steps.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
